\documentclass[hmargin=1.25cm,vmargin=0.75cm,scale=0.9]{deedy-resume-openfont}
\usepackage{fancyhdr}
\usepackage{parskip}
\usepackage{hyperref}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{\thepage}
\fancypagestyle{empty}{
  \fancyhf{}
  \renewcommand{\headrulewidth}{0pt}
}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{David}{Herrera}{\href{mailto:david.herrera83@gmail.com}{david.herrera83@gmail.com} | (385) 268-1173}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 
\subsection{University of Phoenix}
\descript{BS in Information Technology}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\subsection{Programming}
Python \textbullet{} C\# \textbullet{} Appium \textbullet{} Selenium \\
Cypress \textbullet{} Cucumber \textbullet{} MongoDB \\
Automated Pipelines \textbullet{} AWS \textbullet{} SQL \\
CI/CD \textbullet{} Process \& Systems Improvement\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Links} 
Github:// \href{https://github.com/davidherrera83}{\bf davidherrera83} \\
LinkedIn:// \href{https://www.linkedin.com/in/davidherrera83}{\bf davidherrera83} \\
Web:// \href{https://www.herrera-homestead.com}{\bf herrera-homestead.com} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Awards} 
2020 Inspire Award \\
2017 Phoenix Scholarship \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Volunteering
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Volunteering}
\subsection{QA at the Point}
\descript{Board Member}
\location{A meetup for manual \& automation QA professionals}
\subsection{Wasatch Forensic Nurses}
\descript{IT Consultant}
\location{IT Services \& Digital Transformation}
\subsection{Mountainland College}
\descript{Advisory Board Member}
\location{Selected as a member of the Advisory Board for Mountainland Technical College}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Business
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}
\subsection{Herrera Homestead}
\descript{Founder/CTO}
\location{Family enterprise that fosters generational wealth and community prosperity through innovative, automated business solutions and real estate investment.}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}

\runsubsection{Hudl}
\descript{| Senior Management, Quality Assurance }
\location{Sept 2022 - May 2024 | Lincoln, NE}
\begin{tightemize}
\item \textbf{Architected and maintained comprehensive QA processes}, documentation, and tools for Business Operations \& Finance, resulting in a 25\% increase in operational efficiency.
\item \textbf{Hands-on Leadership:} Conducted code reviews, mentored team members, and contributed to coding.
\item \textbf{Developed a learning platform} for Junior QA and Support teams to enhance automation skills.
\item \textbf{Collaborated with cross-functional teams,} reducing project timelines by 20\%.
\item \textbf{Ensured high-quality standards} throughout project phases, achieving 98\% satisfaction.
\end{tightemize}

\runsubsection{MX}
\descript{| Automation Team Lead }
\location{July 2021 - Sept 2022 | Lehi, UT}
\begin{tightemize}
\item \textbf{Developed and executed enterprise-level automation strategy,} reducing manual testing efforts by 40\% and increasing testing efficiency by 35\%, leading to significant operational improvements.
\item \textbf{Led comprehensive training and mentorship programs} for manual QA engineers, achieving a 35\% increase in test automation coverage and a 25\% reduction in testing time, fostering a highly skilled team.
\item \textbf{Established and maintained key cross-functional relationships,} gathering essential automation requirements and reducing project delays by 20\%, ensuring smooth project execution.
\item \textbf{Defined and implemented critical tools and resources,} building a top-tier automation team and solidifying MX's position as an industry leader in automation.
\end{tightemize}

\runsubsection{NICE InContact}
\descript{| Software Engineer in Test }
\location{January 2019 - July 2021 | Sandy, UT}
\begin{tightemize}
\item \textbf{Spearheaded quality assurance initiatives} for the digital multi-channel team, increasing product quality by 25\% and reducing post-release defects by 30\%.
\item \textbf{Mentored and guided QA engineers} in testing, resulting in a 20\% increase in team expertise and a 40\% reduction in onboarding time for new team members.
\item \textbf{Monitored and reported pivotal metrics} such as defect density, test coverage, and test execution efficiency, achieving a 98\% adherence to quality benchmarks and enabling data-driven decision-making.
\end{tightemize}

\runsubsection{Autopoint}
\descript{| QA Lead }
\location{January 2017 - January 2019 | South Jordan, UT}
\begin{tightemize}
\item \textbf{Led QA efforts} for SaaS, backend, and mobile applications, developing comprehensive test plans, test cases, and procedures to ensure top-quality delivery.
\item \textbf{Implemented automated testing frameworks} to streamline testing processes and improve efficiency.
\item \textbf{Collaborated with cross-functional teams,} maintaining high standards of quality and ensuring seamless integration and deployment of updates.
\end{tightemize}

\runsubsection{Ghostery}
\descript{| QA Engineer }
\location{November 2015 - November 2016 | Sandy, UT}
\begin{tightemize}
\item \textbf{Ensured the quality} of SaaS, Web Apps, and mobile applications by designing, executing, and maintaining test plans and test cases.
\item \textbf{Developed efficient testing processes} to validate functionality, performance, security, and scalability of products.
\item \textbf{Conducted mobile testing using Appium}, ensuring robust and reliable mobile application performance.
\end{tightemize}

\end{minipage}
\end{document}
